\documentclass[usenames,dvipsnames,aspectratio=169]{beamer}
\usepackage[utf8]{inputenc}
\usecolortheme{seahorse}
\usepackage{enumitem,amsmath,xfrac,dsfont,amsfonts,bbm,cancel,euler,ulem}
\usepackage{apacite,natbib}
\usepackage{hyperref}
\usepackage{caption,subcaption,booktabs,multicol,adjustbox}
\usepackage{xcolor}


\title{The Rise of American Ingenuity: Innovation and Inventors of the Golden Age \\ \small{Firm Dynamics and Economic Growth} }
\author{Authors: Ufuk Akcigit \and John Grigsby \and Tom Nicholas \\ Presented by: Jose M. Quintero}



\AtBeginSection[]
{
  \begin{frame}<beamer>
    \frametitle{Outline}
    \tableofcontents[currentsection]
  \end{frame}
}

\AtBeginSubsection[]
{
   \begin{frame}
        \frametitle{Outline}
        \tableofcontents[currentsubsection]
   \end{frame}
}



\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{This paper}
\begin{itemize}[label=\textcolor{teal}{$\blacktriangleright$}]
	\item Archive work to create a micro database on patenting in the early XX century
	\begin{enumerate}[label=\textbf{\textcolor{teal}{\arabic*.}}]
		\item Digitize USPTO patents
		\item Merge with Census data (Inventors)
		\item Merge with regional 
	\end{enumerate}
	\vfill
	\item Present stylized facts  that shed light on innovation during the ``Golden Age.''
	\begin{enumerate}[label=\textbf{\textcolor{teal}{\arabic*.}}]
		\item Characteristics of inventors: Who became an inventor?
		\item Characteristics of innovative hubs: What makes a region fertile for innovation?
	\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}{Where does innovation occurs?}{Regional Characteristics}
\begin{enumerate}[label=\textcolor{teal}{R\arabic*.}]
\vfill
\item More inventive states and sectors grew faster on average  
\vfill
\item Densely-populated states were more inventive. 
\vfill
\item Financially-developed states were more inventive.
\vfill
\item Geographically-connected states were more inventive.
\vfill
\item States associated with slavery were less inventive, but religiosity is not robustly correlated with inventiveness.
\vfill
\item Innovation was strongly positively correlated with social mobility.
\vfill
\item Broad measures of income inequality, such as 90/10 ratio, and Gini coefficient, were negatively correlated with innovation.
\vfill
\end{enumerate}
\end{frame}

\begin{frame}[allowframebreaks]{Who becomes an inventor?}{Personal Characteristics}
\begin{enumerate}[label=\textcolor{teal}{I\arabic*.}]
\vfill
\item Inventors were more educated on average and were most productive between the age of 36 and 55.
\vfill
\item Inventors were positively selected through exit early in their careers, but were less productive and more likely to exit late in their careers.
\vfill
\item The patents of new inventors received more citations on average, and were more likely to be in the top decile of the citations distribution.
\vfill
\item Inventors delayed marriage and had fewer children.
\vfill

\framebreak

\vfill
\item Inventors were more likely to have migrated from their state of birth. They moved to states that were more conducive to innovation.
\vfill
\item Father's income was correlated with becoming an inventor. This effect disappears once child's education is controlled for.
\vfill
\item Successful patentees had substantially higher labor income, even controlling for demographics and education.
\vfill
\item Inventor's income was highly correlated with the quality of invention measured by patent citations.
\vfill
\end{enumerate}
\end{frame}

\begin{frame}{What's next?}
\begin{itemize}[label=\textcolor{teal}{$\blacktriangleright$}]
\vfill
\item Facts presented suggest some mechanisms:
\begin{enumerate}[label=\textcolor{teal}{\textbf{(\arabic*.)}}]
\item Agglomeration effects: R2
\item Financial frictions: R3, R6, R7, I6
\item Education: I6
\item Idea flows: R4, R5, I5
\end{enumerate}
\vfill
\item Build a model to understand the mechanisms:
\begin{enumerate}[label=\textcolor{teal}{\textbf{(\arabic*.)}}]
\item Trade-offs
\item Quantify the mechanism
\item Counterfactual analysis for policy design 
\end{enumerate}
\vfill
\end{itemize}

\end{frame}

\end{document}

